---
title: "Analysis and Modeling"
author: "Di Zhou"
date: "06/26/2021"
output: html_document
---

# Code for replicating modeling results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(MASS)
library(pscl)
library(stargazer)
library(table1)
library(scales)

# display digits instead of scientific notation
options(scipen = 999)
```

### Import data

```{r import data}

df_model_rep <- read.csv("data/df_model_rep.csv") # 75079 obs

```

### Correlation table

```{r }

# No continuous emotionality
M <- df_model_rep %>% 
  dplyr::select(answer_upvote,
                nov_std_min0win20,
                author_followerCount_log,
                TTR,
                eng_ratio,
                answer_nchar_strd) %>%
  rename(
    `Answer Upvote` = answer_upvote,
    `Novelty` = nov_std_min0win20,
    `Author Follwer (Logged)` = author_followerCount_log, 
    `Answer Length` = answer_nchar_strd,
    `Lexicon Diversity` = TTR,
    `Eng Usage` = eng_ratio
  )

corr <- round(cor(M), 4)
as.data.frame(corr)


# Including continuous emotionality
M2 <- df_model_rep %>% 
  dplyr::select(answer_upvote,
                nov_std_min0win20,
                emo,
                author_followerCount_log,
                TTR,
                eng_ratio,
                answer_nchar_strd) %>%
  rename(
    `Answer Upvote` = answer_upvote,
    `Novelty` = nov_std_min0win20,
    `Emotionality` = emo,
    `Author Follwer (Logged)` = author_followerCount_log, 
    `Answer Length` = answer_nchar_strd,
    `Lexicon Diversity` = TTR,
    `Eng Usage` = eng_ratio
  )

corr2 <- round(cor(M2), 4)
as.data.frame(corr2)

```

### Descriptive table

```{r descriptive table}

# A Df from group tabulation based whether a post has zero upvote
tab_chrono <-  df_model_rep

# Tab upvote with top writer: suggest seperate problem, should be removed from hurdle model
# table(tab_chrono$answer_upvote_ifzero, tab_chrono$author_if_topwriter)
# table(tab_chrono$q_topic)

# Testing differences between zero & nonzero groups:
tab_chrono_zero <- tab_chrono %>% filter(answer_upvote_ifzero == 1)
tab_chrono_nonzero <- tab_chrono %>% filter(answer_upvote_ifzero == 0)

# Descriptive stats table
# http://thatdatatho.com/2018/08/20/easily-create-descriptive-summary-statistic-tables-r-studio/
table1::label(tab_chrono$answer_upvote) <- "Answer Upvote"
table1::label(tab_chrono$nov_std_min0win20) <- "Novelty Score (Standardised)"
table1::label(tab_chrono$sentiment_cat) <- "Emotionality"
table1::label(tab_chrono$author_followerCount_log) <- "Author Follower Count (In thousand and logged)"
table1::label(tab_chrono$author_if_topwriter) <- "If Author is Top Writer"
table1::label(tab_chrono$answer_nchar_strd) <- "Answer Length (Num of character, standardised)"
table1::label(tab_chrono$TTR) <- "Lexicon Diversity ( Type Token Ratio)"
table1::label(tab_chrono$eng_ratio) <- "English Usage (# of Eng Words/Total English Words + Chinese Character)"
table1::label(tab_chrono$q_answerCount_log) <- "Question Anaswer Count (In hundred and logged)"
table1::label(tab_chrono$q_viewCount_log) <- "Question View Count (In million and logged)"
table1::label(tab_chrono$author_gender) <- "Author Gender"
table1::label(tab_chrono$ele_distance) <- "Time Distance to Election (In day)"
table1::label(tab_chrono$q_topic) <- "Topic Category of the Question"

table1(~answer_upvote + 
                 nov_std_min0win20 +
                 emo +
                 sentiment_cat +
                 author_followerCount_log +
                 author_if_topwriter + 
                 answer_nchar_strd +
                 TTR +
                 eng_ratio +
                 #q_answerCount_log +
                 #q_viewCount_log + 
                 author_gender +
                 ele_distance +
                 q_topic | answer_upvote_ifzero, 
               data = tab_chrono, round_pad = 3)


# The statistics for q_answerCount_log and q_viewCount_log need to replaced 
# by the following result b/c duplicate question IDs need to be removed

# Question's Answer Count and Question's View Count Stats: By group
q_stats_group <- df_model_rep %>%
  group_by(answer_upvote_ifzero) %>%
  distinct(q_id, .keep_all = TRUE) %>%
  summarise(answer_count_mean = mean(q_answerCount_log),
            answer_count_sd = sd(q_answerCount_log),
            answer_count_median = median(q_answerCount_log),
            answer_count_max = max(q_answerCount_log),
            answer_count_min = min(q_answerCount_log),
            view_count_mean = mean(q_viewCount_log),
            view_count_sd = sd(q_viewCount_log),
            view_count_median = median(q_viewCount_log),
            view_count_max = max(q_viewCount_log),
            view_count_min = min(q_viewCount_log)) %>%
  t()

# Question's Answer Count and Question's View Count Stats: Overall
q_stats_ttl <- df_model_rep %>%
  distinct(q_id, .keep_all = TRUE) %>%
  summarise(answer_count_mean = mean(q_answerCount_log),
            answer_count_sd = sd(q_answerCount_log),
            answer_count_median = median(q_answerCount_log),
            answer_count_max = max(q_answerCount_log),
            answer_count_min = min(q_answerCount_log),
            view_count_mean = mean(q_viewCount_log),
            view_count_sd = sd(q_viewCount_log),
            view_count_median = median(q_viewCount_log),
            view_count_max = max(q_viewCount_log),
            view_count_min = min(q_viewCount_log)) %>%
  t()


```



### ZINB model

```{r }
# Since TTR and Eng Ratio are measured at a small scale (from 0 to 1), to show all coefficients clearly
# rescale TTR and Eng Ratio to a scale from 0 to 10. 

df_model_clean_x10 <- df_model_rep %>% 
  mutate(TTR = 10*TTR,
         eng_ratio = 10*eng_ratio,
         sentiment = 10*sentiment,
         emo = 10*emo) %>%
  mutate(TTR_sq = TTR^2,
         eng_ratio_sq = eng_ratio^2,
         sentiment_sq = sentiment^2,
         emo_sq = emo^2)

# Model 1: Novelty linear: novelty(min0win20, standardized), emotion, author follower, author topwriter
m1 <- hurdle(answer_upvote ~ nov_std_min0win20 + 
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_if_topwriter,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 2: M1 + nov^2 (check if curvilinear hypo of nov applies to data)
m2 <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_if_topwriter,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 3: M2 + TTR + Eng
m3 <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_if_topwriter +
                         TTR + eng_ratio,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 4: M3 + Length 
m4 <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_if_topwriter +
                         TTR + eng_ratio + answer_nchar_strd,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 5: M4 + sq terms for TTR & eng ratio & author followers 
m5 <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
                         TTR + TTR_sq + eng_ratio + eng_ratio_sq + answer_nchar_strd,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 6: key IV, all controls
m6 <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
                         TTR + TTR_sq +
                         eng_ratio + eng_ratio_sq +
                         answer_nchar_strd +
                         author_female + author_gender_unknown + 
                         ele_distance +
                         q_viewCount_log + q_answerCount_log + 
                         q_topic_election + q_topic_CNcompare + q_topic_USpolitic + q_topic_USsociety,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Add BIC
m1$BIC <- BIC(m1)
m2$BIC <- BIC(m2)
m3$BIC <- BIC(m3)
m4$BIC <- BIC(m4)
m5$BIC <- BIC(m5)
m6$BIC <- BIC(m6)

# Display
stargazer(m1, m2, m3, m4,  m5, m6, 
          type = "text", 
          #zero.component = TRUE
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          keep.stat = c("bic", "n"),
          notes = "To show coefficients, Lexicon Diversity and English Usage have been timed by 10 since their original measuring scale has a small range compared to other variables.")

```

### Coefficient Plot

```{r }

coef_df <- ggstatsplot::ggcoefstats(x = m6, output = "tidy")

# Keep only count component
## Rename term names for plotting
new_term <- c("Extremely Positive", "Moderately Positive", "Slightly Positive",
              "Slightly Negative", "Moderately Negative", "Extremely Negative")

coef_df_plot <- coef_df %>%
  filter(str_detect(term, "count_sen")) %>%
  mutate(p.value = round(p.value, 3),
         term = new_term) %>% 
  arrange(-row_number()) # Reverse row orders for plotting

ggstatsplot::ggcoefstats(
  x = coef_df_plot,
  statistic = "z",
  only.significant = FALSE,
  conf.level = 0.99,
  stats.labels = FALSE,
  point.args = list(color = "black", size = 1),
  vline.args = list(size = 0.5, linetype = "dashed")
) +
  ggplot2::labs(x = "Coefficients", y = NULL) +
  theme_classic()

# ggsave("graph/coef_plot_emodum_rr.png", width = 8, height = 5)


```

### Novelty: Dummy up to check curvilinearity 

```{r }
# If novelty is curvilinear, the effect should be highest on middle cut
df_model_clean_dum <- df_model_clean_x10

# Defind cut breaks
dum_break <- c(-2, seq( -0.5, 0, 0.1), seq( 1, 5, 1), 7, 9, 13, 18) #use this
# Create variable
df_model_clean_dum$novelty_cut <- cut(df_model_clean_dum$nov_std_min0win20, breaks = dum_break)
# Check distribution
table(df_model_clean_dum$novelty_cut)

# Model
m_nov_dum <- hurdle(answer_upvote ~ novelty_cut +
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
                         TTR + TTR_sq + 
                         eng_ratio + eng_ratio_sq +
                         answer_nchar_strd + 
                         author_gender + 
                         ele_distance +
                         q_viewCount_log + q_answerCount_log + q_topic,
             data = df_model_clean_dum,
             dist = "negbin", zero.dist = "binomial")

m_nov_dum$BIC <- BIC(m_nov_dum)

# Display model
stargazer(m_nov_dum, 
          type = "text", 
          keep.stat = c("n", "BIC"), 
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001))

# Plot coefficients
coef_df_dum <- ggstatsplot::ggcoefstats(x = m_nov_dum, output = "tidy")
coef_dum_plot <- coef_df_dum %>%
  filter(str_detect(term, "count_novelty_cut")) %>%
  mutate(p.value = round(p.value, 3), 
         term = str_remove(term, "^count_novelty_cut"))

ggstatsplot::ggcoefstats(
  x = coef_dum_plot,
  statistic = "z",
  #sort = "ascending",
  only.significant = FALSE,
  conf.level = 0.95,
  stats.labels = FALSE,
  point.args = list(color = "black", size = 1),
  vline.args = list(size = 0.5, linetype = "dashed"),
  title = "Coefficients of Novelty Dummies (Using Model 6, Ref: Novelty ≤ -0.5)",
  ylab = "Novelty Z-Score"
)
# ggsave("graph/coef_novelty_dummies_min0_rr.png", width = 8, height = 4)


# Adjust z-score bins level
levels(coef_dum_plot$term)
coef_dum_plot$term <- factor(coef_dum_plot$term,
                             levels = c("(-0.5,-0.4]",
                                        "(-0.4,-0.3]",
                                        "(-0.3,-0.2]",
                                        "(-0.2,-0.1]",
                                        "(-0.1,0]",
                                        "(0,1]",
                                        "(1,2]",
                                        "(2,3]",
                                        "(3,4]",
                                        "(4,5]",
                                        "(5,7]",
                                        "(7,9]",
                                        "(9,13]",
                                        "(13,18]"))

tt <- coef_dum_plot %>%
  mutate(range_left = as.numeric(str_extract(term, "(?<=\\()\\S+(?=\\,)")),
         range_right = as.numeric(str_extract(term, "(?<=\\,)\\S+(?=\\])"))) %>%
  mutate(range_midpoint = (range_left + range_right)/2)

tt %>% ggplot() +
  geom_point(data = tt, aes(x = range_midpoint, y = estimate)) +
  geom_line(data = tt, aes(x = range_midpoint, y = estimate), size = 0.5, color = "grey50") +
  geom_errorbar(data = tt, aes(x = range_midpoint, y = estimate, ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(data = tt, yintercept = 0, linetype = "dashed") + 
  labs(x = "Novelty z-score", y = "Coefficients of Novelty Dummies") + 
  scale_x_continuous(breaks = seq(-2, 18, 2)) +
  geom_rug(data = df_model_rep, aes(nov_std_min0win20), sides = "b", color = "grey50") +
  theme_linedraw()

# ggsave("graph/coef_novelty_dummies_rotated_rr.png", width = 8, height = 4)

```

### Plot marginal effect: Novelty

```{r }
# Create dataframe of Yhat for plotting effects
# Let key X vary, other Xs fixed at mean
pred_nov <- expand.grid(nov_std_min0win20 = seq(-2, 18, 1)) %>% 
  mutate(nov_std_sq_min0win20 = nov_std_min0win20^2, 
         sen_pos_ext = mean(df_model_clean_x10$sen_pos_ext),
         sen_pos_mod = mean(df_model_clean_x10$sen_pos_mod),
         sen_pos_sli = mean(df_model_clean_x10$sen_pos_sli),
         sen_neg_sli = mean(df_model_clean_x10$sen_neg_sli),
         sen_neg_mod = mean(df_model_clean_x10$sen_neg_mod),  
         sen_neg_ext = mean(df_model_clean_x10$sen_neg_ext),
         author_followerCount_log = mean(df_model_clean_x10$author_followerCount_log),
         author_followerCount_log_sq = author_followerCount_log^2,
         author_if_topwriter = mean(df_model_clean_x10$author_if_topwriter),
         answer_nchar_strd = 0,
         TTR = mean(df_model_clean_x10$TTR),
         TTR_sq = TTR^2,
         eng_ratio = mean(df_model_clean_x10$eng_ratio),
         eng_ratio_sq = eng_ratio^2,
         author_female = mean(df_model_clean_x10$author_female),
         author_gender_unknown = mean(df_model_clean_x10$author_gender_unknown),
         ele_distance = mean(df_model_clean_x10$ele_distance),
         q_answerCount_hundred = mean(df_model_clean_x10$q_answerCount_hundred),
         q_answerCount_log = mean(df_model_clean_x10$q_answerCount_log),
         q_viewCount_million = mean(df_model_clean_x10$q_viewCount_million),
         q_viewCount_log = mean(df_model_clean_x10$q_viewCount_log),
         q_topic_election = mean(df_model_clean_x10$q_topic_election),
         q_topic_CNcompare = mean(df_model_clean_x10$q_topic_CNcompare),
         q_topic_USpolitic = mean(df_model_clean_x10$q_topic_USpolitic),
         q_topic_USsociety = mean(df_model_clean_x10$q_topic_USsociety))

# Models: m3, m5, m6
pred_nov$predicted_upvote_m3 <- predict(m3, pred_nov) # Key IVs
pred_nov$predicted_upvote_m5<- predict(m5, pred_nov)  # Key IVs + square for TTR, Eng + length
pred_nov$predicted_upvote_m6 <- predict(m6, pred_nov) # All 

plot_effect_nov <- ggplot() +
  geom_point(data = pred_nov, aes(x = nov_std_min0win20, y = predicted_upvote_m6), size = 1) + 
  geom_line(data = pred_nov, aes(x = nov_std_min0win20, y = predicted_upvote_m6), linetype = "solid") +
  geom_point(data = pred_nov, aes(x = nov_std_min0win20, y = predicted_upvote_m5), size = 1) +
  geom_line(data = pred_nov, aes(x = nov_std_min0win20, y = predicted_upvote_m5), linetype = "dashed") +
  geom_point(data = pred_nov, aes(x = nov_std_min0win20, y = predicted_upvote_m3), size = 1) +
  geom_line(data = pred_nov, aes(x = nov_std_min0win20, y = predicted_upvote_m3), linetype = "dotted") +
  geom_rug(data = df_model_rep, aes(nov_std_min0win20), sides = "b", color = "grey50") + 
  scale_y_continuous(limits = c(0, 250), breaks = seq(0, 250, 25)) +
  scale_x_continuous(limits = c(-2, 18), breaks = seq(-2, 18, 2)) +
  labs(x = "Novelty", y = "Expected upvotes", color = "Model") +
  theme_classic()
  
plot_effect_nov
# ggsave("graph/pred_novelty_min0_rr.png", height = 7, width = 10)


```

### Plot effect of author followers

```{r }

# Create dataframe of Yhat for plotting effects
# Let key X vary, other Xs fixed at mean
pred_author <- expand.grid(author_followerCount_thous = seq(0.001, 500, 25)) %>% 
  mutate(author_followerCount_log = log(author_followerCount_thous),
         author_followerCount_log_sq = author_followerCount_log^2,
         nov_std_min0win20 = 0,
         nov_std_sq_min0win20 = nov_std_min0win20^2, 
         sen_pos_ext = mean(df_model_clean_x10$sen_pos_ext),
         sen_pos_mod = mean(df_model_clean_x10$sen_pos_mod),
         sen_pos_sli = mean(df_model_clean_x10$sen_pos_sli),
         sen_neg_sli = mean(df_model_clean_x10$sen_neg_sli),
         sen_neg_mod = mean(df_model_clean_x10$sen_neg_mod),  
         sen_neg_ext = mean(df_model_clean_x10$sen_neg_ext),
         author_if_topwriter = mean(df_model_clean_x10$author_if_topwriter),
         answer_nchar_strd = 0,
         TTR = mean(df_model_clean_x10$TTR),
         TTR_sq = TTR^2,
         eng_ratio = mean(df_model_clean_x10$eng_ratio),
         eng_ratio_sq = eng_ratio^2,
         author_female = mean(df_model_clean_x10$author_female),
         author_gender_unknown = mean(df_model_clean_x10$author_gender_unknown),
         ele_distance = mean(df_model_clean_x10$ele_distance),
         q_answerCount_hundred = mean(df_model_clean_x10$q_answerCount_hundred),
         q_answerCount_log = mean(df_model_clean_x10$q_answerCount_log),
         q_viewCount_million = mean(df_model_clean_x10$q_viewCount_million),
         q_viewCount_log = mean(df_model_clean_x10$q_viewCount_log),
         q_topic_election = mean(df_model_clean_x10$q_topic_election),
         q_topic_CNcompare = mean(df_model_clean_x10$q_topic_CNcompare),
         q_topic_USpolitic = mean(df_model_clean_x10$q_topic_USpolitic),
         q_topic_USsociety = mean(df_model_clean_x10$q_topic_USsociety))

# Models: 
pred_author$predicted_upvote_m3 <- predict(m3, pred_author)
pred_author$predicted_upvote_m5 <- predict(m5, pred_author)
pred_author$predicted_upvote_m6 <- predict(m6, pred_author)

plot_effect_authorfol <- ggplot() +
  geom_point(data = pred_author, aes(x = author_followerCount_thous, y = predicted_upvote_m6), size = 1) + 
  geom_line(data = pred_author, aes(x = author_followerCount_thous, y = predicted_upvote_m6), linetype = "solid") +
  geom_point(data = pred_author, aes(x = author_followerCount_thous, y = predicted_upvote_m5), size = 1) +
  geom_line(data = pred_author, aes(x = author_followerCount_thous, y = predicted_upvote_m5), linetype = "dashed") +
  geom_point(data = pred_author, aes(x = author_followerCount_thous, y = predicted_upvote_m3), size = 1) +
  geom_line(data = pred_author, aes(x = author_followerCount_thous, y = predicted_upvote_m3), linetype = "dotted") +
  geom_rug(data = df_model_rep, aes(author_followerCount_thous), sides = "b", color = "grey50") +
  scale_x_continuous(limits = c(0, 500), breaks = seq(0, 500, 50)) +
  labs(x = "Author Follower Count (in 1,000)", y = "") +
  theme_classic() +
  theme(legend.position = "bottom")

plot_effect_authorfol
# ggsave("graph/pred_author_rr.png", height = 7, width = 10)

```

### Plot effect of TTR

```{r }
# Create dataframe of Yhat for plotting effects
# Let key X vary, other Xs fixed at mean
pred_ttr <- expand.grid(TTR = seq(0, 10, 0.5)) %>% 
  mutate(TTR_sq = TTR^2,
         nov_std_min0win20 = 0,
         nov_std_sq_min0win20 = nov_std_min0win20^2, 
         sen_pos_ext = mean(df_model_clean_x10$sen_pos_ext),
         sen_pos_mod = mean(df_model_clean_x10$sen_pos_mod),
         sen_pos_sli = mean(df_model_clean_x10$sen_pos_sli),
         sen_neg_sli = mean(df_model_clean_x10$sen_neg_sli),
         sen_neg_mod = mean(df_model_clean_x10$sen_neg_mod),  
         sen_neg_ext = mean(df_model_clean_x10$sen_neg_ext),
         author_followerCount_log = mean(df_model_clean_x10$author_followerCount_log),
         author_followerCount_log_sq = author_followerCount_log^2,
         author_if_topwriter = mean(df_model_clean_x10$author_if_topwriter),
         answer_nchar_strd = 0,
         eng_ratio = mean(df_model_clean_x10$eng_ratio),
         eng_ratio_sq = eng_ratio^2,
         author_female = mean(df_model_clean_x10$author_female),
         author_gender_unknown = mean(df_model_clean_x10$author_gender_unknown),
         ele_distance = mean(df_model_clean_x10$ele_distance),
         q_answerCount_hundred = mean(df_model_clean_x10$q_answerCount_hundred),
         q_answerCount_log = mean(df_model_clean_x10$q_answerCount_log),
         q_viewCount_million = mean(df_model_clean_x10$q_viewCount_million),
         q_viewCount_log = mean(df_model_clean_x10$q_viewCount_log),
         q_topic_election = mean(df_model_clean_x10$q_topic_election),
         q_topic_CNcompare = mean(df_model_clean_x10$q_topic_CNcompare),
         q_topic_USpolitic = mean(df_model_clean_x10$q_topic_USpolitic),
         q_topic_USsociety = mean(df_model_clean_x10$q_topic_USsociety))

# Models: 
pred_ttr$predicted_upvote_m3 <- predict(m3, pred_ttr)
pred_ttr$predicted_upvote_m5 <- predict(m5, pred_ttr)
pred_ttr$predicted_upvote_m6 <- predict(m6, pred_ttr)

# Plot
plot_effect_ttr <- ggplot() +
  geom_point(data = pred_ttr, aes(x = TTR, y = predicted_upvote_m6), size = 1) + 
  geom_line(data = pred_ttr, aes(x = TTR, y = predicted_upvote_m6), linetype = "solid") +
  geom_point(data = pred_ttr, aes(x = TTR, y = predicted_upvote_m5),  size = 1) +
  geom_line(data = pred_ttr, aes(x = TTR, y = predicted_upvote_m5), linetype = "dashed") +
  geom_point(data = pred_ttr, aes(x = TTR, y = predicted_upvote_m3),  size = 1) +
  geom_line(data = pred_ttr, aes(x = TTR, y = predicted_upvote_m3), linetype = "dotted") +
  geom_rug(data = df_model_clean_x10, aes(TTR), sides = "b", color = "grey50") +
  scale_y_continuous(limits = c(0, 250), breaks = seq(0, 250, 25)) +
  scale_x_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
  labs(x = "Lexical Diversity", y = "Expected Upvotes") +
  theme_classic() +
  theme(legend.position = "none")

plot_effect_ttr
# ggsave("graph/pred_ttr_rr.png", height = 7, width = 10)

```

### Plot effect of Eng Ratio

```{r }
# Create dataframe of Yhat for plotting effects
# Let key X vary, other Xs fixed at mean
pred_eng <- expand.grid(eng_ratio = seq(0, 10, 0.5)) %>% 
  mutate(eng_ratio_sq = eng_ratio^2,
         nov_std_min0win20 = 0,
         nov_std_sq_min0win20 = nov_std_min0win20^2, 
         sen_pos_ext = mean(df_model_clean_x10$sen_pos_ext),
         sen_pos_mod = mean(df_model_clean_x10$sen_pos_mod),
         sen_pos_sli = mean(df_model_clean_x10$sen_pos_sli),
         sen_neg_sli = mean(df_model_clean_x10$sen_neg_sli),
         sen_neg_mod = mean(df_model_clean_x10$sen_neg_mod),  
         sen_neg_ext = mean(df_model_clean_x10$sen_neg_ext),
         author_followerCount_log = mean(df_model_clean_x10$author_followerCount_log),
         author_followerCount_log_sq = author_followerCount_log^2,
         author_if_topwriter = mean(df_model_clean_x10$author_if_topwriter),
         answer_nchar_strd = 0,
         TTR = mean(df_model_clean_x10$TTR),
         TTR_sq = TTR^2,
         author_female = mean(df_model_clean_x10$author_female),
         author_gender_unknown = mean(df_model_clean_x10$author_gender_unknown),
         ele_distance = mean(df_model_clean_x10$ele_distance),
         q_answerCount_hundred = mean(df_model_clean_x10$q_answerCount_hundred),
         q_answerCount_log = mean(df_model_clean_x10$q_answerCount_log),
         q_viewCount_million = mean(df_model_clean_x10$q_viewCount_million),
         q_viewCount_log = mean(df_model_clean_x10$q_viewCount_log),
         q_topic_election = mean(df_model_clean_x10$q_topic_election),
         q_topic_CNcompare = mean(df_model_clean_x10$q_topic_CNcompare),
         q_topic_USpolitic = mean(df_model_clean_x10$q_topic_USpolitic),
         q_topic_USsociety = mean(df_model_clean_x10$q_topic_USsociety))

# Models:
pred_eng$predicted_upvote_m3 <- predict(m3, pred_eng)
pred_eng$predicted_upvote_m5 <- predict(m5, pred_eng)
pred_eng$predicted_upvote_m6 <- predict(m6, pred_eng)

plot_effect_eng <- ggplot() +
  geom_point(data = pred_eng, aes(x = eng_ratio, y = predicted_upvote_m6), size = 1) + 
  geom_line(data = pred_eng, aes(x = eng_ratio, y = predicted_upvote_m6, linetype = "Model 6 (Final Model)")) +
  geom_point(data = pred_eng, aes(x = eng_ratio, y = predicted_upvote_m5), size = 1) +
  geom_line(data = pred_eng, aes(x = eng_ratio, y = predicted_upvote_m5, linetype = "Model 5")) +
  geom_point(data = pred_eng, aes(x = eng_ratio, y = predicted_upvote_m3), size = 1) +
  geom_line(data = pred_eng, aes(x = eng_ratio, y = predicted_upvote_m3, linetype = "Model 3")) +
  geom_rug(data = df_model_clean_x10, aes(eng_ratio), sides = "b", color = "grey50") +
  scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, 20)) +
  scale_x_continuous(limits = c(0, 10), breaks = seq(0, 10, 2)) +
  labs(x = "English Usage", y = "", linetype = "Model") +
  scale_linetype_manual(values=c("dotted", "dashed", "solid")) +
  theme_classic() +
  theme(legend.position = "none") #+
   #theme(legend.position = "bottom",
         #legend.title = element_text(size = 10),
         #legend.text = element_text(size = 10))

plot_effect_eng
# ggsave("graph/plot_effect_eng_rr.png", height = 7, width = 10)

```

### Plot effect of emotionality

```{r }
pred_sen <- tibble(sen_pos_ext = c(1, 0, 0, 0, 0, 0 ,0),
            sen_pos_mod = c(0, 1, 0, 0, 0, 0, 0),
            sen_pos_sli = c(0, 0, 1, 0, 0, 0, 0),
            sen_neg_sli = c(0, 0, 0, 0, 1, 0, 0),
            sen_neg_mod = c(0, 0, 0, 0, 0, 1, 0),
            sen_neg_ext = c(0, 0, 0, 0, 0, 0, 1)) %>%
  mutate(
         nov_std_min0win20 = 0,
         nov_std_sq_min0win20 = nov_std_min0win20^2, 
         author_followerCount_log = mean(df_model_clean_x10$author_followerCount_log),
         author_followerCount_log_sq = author_followerCount_log^2,
         author_if_topwriter = mean(df_model_clean_x10$author_if_topwriter),
         answer_nchar_strd = 0,
         TTR = mean(df_model_clean_x10$TTR),
         TTR_sq = TTR^2,
         eng_ratio = mean(df_model_clean_x10$eng_ratio),
         eng_ratio_sq = eng_ratio^2,
         author_female = mean(df_model_clean_x10$author_female),
         author_gender_unknown = mean(df_model_clean_x10$author_gender_unknown),
         ele_distance = mean(df_model_clean_x10$ele_distance),
         q_answerCount_hundred = mean(df_model_clean_x10$q_answerCount_hundred),
         q_answerCount_log = mean(df_model_clean_x10$q_answerCount_log),
         q_viewCount_million = mean(df_model_clean_x10$q_viewCount_million),
         q_viewCount_log = mean(df_model_clean_x10$q_viewCount_log),
         q_topic_election = mean(df_model_clean_x10$q_topic_election),
         q_topic_CNcompare = mean(df_model_clean_x10$q_topic_CNcompare),
         q_topic_USpolitic = mean(df_model_clean_x10$q_topic_USpolitic),
         q_topic_USsociety = mean(df_model_clean_x10$q_topic_USsociety))

# Models: m3, m5, m6
pred_sen$predicted_upvote_m3 <- predict(m3, pred_sen)
pred_sen$predicted_upvote_m5 <- predict(m5, pred_sen)
pred_sen$predicted_upvote_m6 <- predict(m6, pred_sen)

# Select predicted value columns, Add category name
pred_sen_pivot <- pred_sen %>%
  dplyr::select(sen_pos_ext, sen_pos_mod, sen_pos_sli, sen_neg_sli, sen_neg_mod, sen_neg_ext,
         predicted_upvote_m3, predicted_upvote_m5, predicted_upvote_m6) %>%
  mutate(sentiment_cat = c("Extremely Positive", "Moderately Positive", "Slightly Positive",
                           "Neutral",
                           "Slightly Negative", "Moderately Negative", "Extremely Negative")) %>%
  pivot_longer(c("predicted_upvote_m3", "predicted_upvote_m5", "predicted_upvote_m6"),
               names_to = "model",
               values_to = "predicted_upvote")

# Set sentiment_cat levels
levels(pred_sen_pivot$sentiment_cat)
pred_sen_pivot$sentiment_cat <- factor(pred_sen_pivot$sentiment_cat,
                                       levels = c("Extremely Negative",
                                                  "Moderately Negative",
                                                  "Slightly Negative",
                                                  "Neutral",
                                                  "Slightly Positive",
                                                  "Moderately Positive",
                                                  "Extremely Positive")
                                       )

levels(pred_sen_pivot$model)
pred_sen_pivot$model <- factor(pred_sen_pivot$model,
                               levels = c("predicted_upvote_m6", 
                                          "predicted_upvote_m3",
                                          "predicted_upvote_m5")
                                       )

addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

plot_effect_emo <- pred_sen_pivot %>%
  ggplot(aes(x = sentiment_cat, y = predicted_upvote, group = model)) +
  geom_point() +
  geom_line(aes(linetype = model)) +
  labs(x = "Emotionality", y = "") +
  scale_x_discrete(
    labels = addline_format(
      c("Extremely Negative",
        "Moderately Negative", 
        "Slightly Negative",
        "Neutral",
        "Slightly Positive", 
        "Moderately Positive", 
        "Extremely Positive")
      )
    ) +
  scale_y_continuous(limits = c(12, 35), breaks = seq(10, 35, 5)) +
  theme_classic() +
  theme(legend.position = "none")

plot_effect_emo  
# ggsave("graph/pred_emo_rr.png", height = 4, width = 6)

```

### Sensitivity Test: Min10Win20

```{r }

# Model using min = 10, win = 20
m6_min10win20 <- hurdle(answer_upvote ~ nov_std_min10win20 + nov_std_sq_min10win20 +
                         sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                         author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
                         TTR + TTR_sq +
                         eng_ratio + eng_ratio_sq +
                         answer_nchar_strd +
                         author_female + author_gender_unknown + 
                         ele_distance +
                         q_viewCount_log + q_answerCount_log + 
                         q_topic_election + q_topic_CNcompare + q_topic_USpolitic + q_topic_USsociety,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

m6_min10win20$BIC <- BIC(m6_min10win20)

# Display
stargazer(m6, m6_min10win20, 
          type = "text", 
          keep.stat = c("n", "BIC"),
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001))

```

### Sensitivity Test: Continuous Emotionality Measures

```{r }

# Model 1: Novelty linear: novelty(min0win20, standardized), emotion, author follower, author topwriter
m1_emo <- hurdle(answer_upvote ~ nov_std_min0win20 + 
                   emo + author_followerCount_log + author_if_topwriter,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 2: M1 + nov^2 (check if curvilinear hypo of nov applies to data)
m2_emo <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                    emo + emo_sq + 
                    author_followerCount_log + author_if_topwriter,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 3: M2 + TTR + Eng
m3_emo <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         emo + emo_sq + 
                         author_followerCount_log + author_if_topwriter +
                         TTR + eng_ratio,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 4: M3 + Length 
m4_emo <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         emo + emo_sq + 
                         author_followerCount_log + author_if_topwriter +
                         TTR + eng_ratio + answer_nchar_strd,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 5: M4 + sq terms for TTR & eng ratio (other sq terms are not significant)
m5_emo <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         emo + emo_sq + 
                         author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
                         TTR + TTR_sq + eng_ratio + eng_ratio_sq + answer_nchar_strd,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")

# Model 6: key IV, all controls
m6_emo <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
                         emo + emo_sq + 
                         author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
                         TTR + TTR_sq +
                         eng_ratio + eng_ratio_sq +
                         answer_nchar_strd +
                         author_female + author_gender_unknown + 
                         ele_distance +
                         q_viewCount_log + q_answerCount_log + 
                         q_topic_election + q_topic_CNcompare + q_topic_USpolitic + q_topic_USsociety,
             data = df_model_clean_x10,
             dist = "negbin", zero.dist = "binomial")


# Add BIC
m1_emo$BIC <- BIC(m1_emo)
m2_emo$BIC <- BIC(m2_emo)
m3_emo$BIC <- BIC(m3_emo)
m4_emo$BIC <- BIC(m4_emo)
m5_emo$BIC <- BIC(m5_emo)
m6_emo$BIC <- BIC(m6_emo)

# Display
stargazer(m1_emo, m2_emo, m3_emo, m4_emo,  m5_emo, m6_emo, 
          type = "text", 
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          keep.stat = c("bic", "n"),
          notes = "To show coefficients, Emotionality, Lexicon Diversity, and English Usage have been timed by 10 since their original measuring scale has a small range compared to other variables.")

```

### Sensitivity Test: Using only US politics Posts

```{r }
# Run regression only on US politics posts
df_model_clean_x10_uspol <- df_model_clean_x10 %>%
  filter(q_topic == "2016美国大选" | q_topic == "美国政治")
# 70784 

# Model 1: Novelty linear: novelty(min0win20, standardized), emotion, author follower, author topwriter
m1_pol <- hurdle(answer_upvote ~ nov_std_min0win20 + 
               sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                 author_followerCount_log + author_if_topwriter,
             data = df_model_clean_x10_uspol,
             dist = "negbin", zero.dist = "binomial")

# Model 2: M1 + nov^2 (check if curvilinear hypo of nov applies to data)
m2_pol <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
               sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                 author_followerCount_log + author_if_topwriter,
             data = df_model_clean_x10_uspol,
             dist = "negbin", zero.dist = "binomial")

# Model 3: M2 + TTR + Eng
m3_pol <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
               sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                 author_followerCount_log + author_if_topwriter +
               TTR + eng_ratio,
             data = df_model_clean_x10_uspol,
             dist = "negbin", zero.dist = "binomial")

# Model 4: M3 + Length 
m4_pol <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
               sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                 author_followerCount_log + author_if_topwriter +
               TTR + eng_ratio + answer_nchar_strd,
             data = df_model_clean_x10_uspol,
             dist = "negbin", zero.dist = "binomial")

# Model 5: M4 + sq terms for TTR & eng ratio (other sq terms are not significant)
m5_pol <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
               sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                 author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
               TTR + TTR_sq + eng_ratio + eng_ratio_sq + answer_nchar_strd,
             data = df_model_clean_x10_uspol,
             dist = "negbin", zero.dist = "binomial")

# Model 6: key IV, all controls
m6_pol <- hurdle(answer_upvote ~ nov_std_min0win20 + nov_std_sq_min0win20 +
               sen_pos_ext + sen_pos_mod + sen_pos_sli + sen_neg_sli + sen_neg_mod + sen_neg_ext + 
                 author_followerCount_log + author_followerCount_log_sq + author_if_topwriter +
               TTR + TTR_sq +
               eng_ratio + eng_ratio_sq +
               answer_nchar_strd +
               author_female + author_gender_unknown + 
               ele_distance +
               q_viewCount_log + q_answerCount_log + 
               q_topic_election,
             data = df_model_clean_x10_uspol,
             dist = "negbin", zero.dist = "binomial")

# Add BIC
m1_pol$BIC <- BIC(m1_pol)
m2_pol$BIC <- BIC(m2_pol)
m3_pol$BIC <- BIC(m3_pol)
m4_pol$BIC <- BIC(m4_pol)
m5_pol$BIC <- BIC(m5_pol)
m6_pol$BIC <- BIC(m6_pol)

# Display
stargazer(m1_pol, m2_pol, m3_pol, m4_pol,  m5_pol, m6_pol, 
          type = "text", 
          star.char = c("*", "**", "***"),
          star.cutoffs = c(0.05, 0.01, 0.001),
          keep.stat = c("bic", "n")
          )

```
